Flaring star-planet interactions in Kepler and TESS

### 2023-05-31 src/tex/ms.tex
[showyourwork] overleaf sync

\subsection{Flaring star-planet interaction signal}
\label{sec:results:spi}
We used the custom Anderson-Darling test introduced in Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations. We choose the $ED$ cutoff to make sure that we are comparing similar flares regardless of spectral type, that is, flares above the same energy relative to stellar luminosity, without losing too many flares. In~\citet{ilin2022searching}, AU Mic appeared to be more modulated with orbital period in the high energy flares above $1\,$s than below. It is also the only star in our sample, for which this threshold makes a difference in the significance of the Anderson-Darling test. However, we note that we lose four systems by applying this threshold -- GJ 393, Kepler-411, Kepler-138, and Kepler-1084. We note that the flares (with $ED<1\,$s) in all of these systems are consistent with random flare phases within $1\sigma$.

@@

The only single star system excluded is GJ 1061. The star is lacking a stellar rotation period estimate, which we need to calculate the magnetic field, and $v_{rel}$. \citet{dreizler2020reddots} estimate that it is a fairly slow rotator with a period between 50 and 200 days, so we do not expect it to have a strong magnetic field anyway.

@@

\subsubsection{Proxima Cen}
\label{sec:results:individualstars:proxima}
We do not detect a deviation from intrinsic flaring on Proxima Cen, consistent with numerical models that place Proxima Cen b well outside the sub-Alfv\'enic zone~\citep{kavanagh2021planetinduced}. However, this might not entirely exclude Proxima Cen from the search for flaring star-planet interaction. The tentatively detected Proxima Cen d, a planet further in, at 0.029 au, or 5 day orbital period~\citep{faria2022candidate, artigau2022linebyline} could still cause flaring star-planet interactions. However, the orbital period of the tentative planet is so uncertain at this point that its coherence time~(Section~\ref{sec:results:coherence}) is shorter than the roughly 2yr observing baseline of Proxima Cen, preventing us from accurately measuring the flare phases.

@@

AU Mic is a 16-29 Myr old pre-main sequence M0-M1 dwarf with a strong magnetic field of about $3010\pm220\,$G obtained from Zeeman broadening measurements~\citep{reiners2022magnetism}. The innermost Neptune-sized planet, AU Mic b, could be both inside the sub-Alfv\'enic zone if the star's mass loss rate is relatively low at about 30 times the solar value or lower. If the mass loss rate is high, exceeding the solar value by a factor of several hundreds, AU Mic b could orbit in the super-Alfv\'enic zone, and become unable to experience any planet-induced flaring. Recently, \citet{klein2022one} found tentative periodicity with the orbital period of AU Mic b in the chromospheric He I D line, which increases if the contribution from flares is included in the calculation. Overall, our marginal signal of flaring star-planet interaction in the AU Mic system supports the idea that this young, magnetically active M dwarf system with a close-in Neptune could exhibit planet-induced flaring.
For a detailed discussion of AU Mic and its flaring star-planet interaction, we refer to~\cite{ilin2022searching}, where we also estimate that an additional 50–100 days of TESS-like monitoring of AU Mic would yield a $3\sigma$ detection if the marginal signal in our data is real.

K2-25 is a multiplanet system around a fast rotating ($P_{\rm rot}<2\,$d) mid-M dwarf in the Hyades open cluster~\citep[600-800 Myr, ][]{stefansson2020habitable}. Both the expected power of interaction, and the measured deviation, are remarkably similar to the AU Mic system. Interestingly, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits~\citep{rockcliffe2021lya}. This might in part be due to the stellar wind conditions around K2-25 b. Further investigation of magnetic star-planet interactions, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius, especially accounting for its moderately high eccentricity~(see also Section~\ref{sec:discussion:eccentricity}).

In Figure~\ref{fig:adtest_bp}, TOI-540 clusters with K2-25 and AU Mic -- a fast rotating M dwarf with its innermost planet in a $1.24\,$d orbit~\citep{ment2021toi}. Compared to the other two systems, its innermost planet is not a Neptune, but a rocky planet slightly smaller than Earth~\citep{ment2021toi}. It is a relatively smaller obstacle in the host's magnetic field, yet the interaction is expected to be of a similar magnitude due to the strongest inferred magnetic field, and closest orbit among the three systems.

@@

\subsubsection{KOI-12}
\label{sec:results:individualstars:koi12}
KOI-12, also known as Kepler-448, is a two-planet system with an eccentric outer planet KOI-12 c, and an inner Warm Jupiter planet KOI-12 b in a $17.8\,$d orbit~\citep{masuda2017eccentric}. With respect to rotation rate, stellar and planetary radius, the KOI-12 system is similar to HIP~67522 and TAP~26 (although for the those young stars the radii are large because the stars are still contracting onto the main sequence). In constrast, KOI-12 is $1.4\pm0.3\,$Gyr old~\citep{bourrier2015sophie}, an F5 subgiant~\citep{frasca2016activity}, which is already evolving off the main sequence. Yet, despite its high expected power of interaction, we detect no excess flaring in phase with KOI-12 b. Here, the reason could be that KOI-12 b is in fact super-Alfv\'enic due to the relatively wide orbit compared to TAP 26 and HIP 67522. Intermittent interaction might play a role here as well, and could be favored if future observations capture episodes during which the interaction is 'on'.

@@

\subsection{Eccentricity}
\label{sec:discussion:eccentricity}
Orbital eccentricity can affect magnetic SPI by modulating the planet's distance to the star. If the planetary orbit is highly eccentric, the difference between periastron and apoastron can be significantly larger than the variability of the Alfv\'en radius. If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, during the planet's rapid periastron passage. This was previously exploited in the case of HD 17156~\citep{maggio2015coordinated}, and analogously for the colliding magnetospheres in binary systems~\citep{massi2002periodic,getman2016search}. In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e\leq 0.35$. The exception is K2-25, with a relatively high $e=0.45$. If periastron passage in K2-25 occurs when the planet is in front of the star relative to the observer, the visibility effect of the interaction footpoint is further increased by the narrow phase range of the periastron passage. \citet{stefansson2020habitable} estimated the argument of periastron $\omega=120^{+12}_{-14}\,$deg for K2-25 (with longitude of the ascending node chosen such that $\omega$ is the same as the longitude of periastron, with $\omega=90\,$deg being periastron passage during transit,~\citealt{kipping2010investigations,dawson2012photoeccentric}). We can therefore conjecture that the tentative signal of flaring SPI in K2-25 is enhanced by eccentricity. Statistically, we are more likely to observe a planetary transit close to periastron, since periastron permits more orbital inclinations than apoastron. So, overall, we expect eccentric transiting systems to experience elevated SPI signal.

@@

Consider a system, where orbit, and stellar spin and stellar magnetic dipole are aligned. If the footpoint's latitude is low, i.e., close to the orbital plane, the orbital plane can be inclined to a high degree, and the footpoint will still periodically move in and out of view. However, if the footpoint's latitude is high, we need to observe the star-planet system nearly edge-on to be able to measure a modulation of activity with the planet's orbital phase. Assuming the dipole field dominates at the distance of the planet, the footpoint will be close to the pole, similar to the UV spot created by Io and the other moons in the polar cap of Jupiter~\citep{clarke1996farultraviolet, prange1996rapid}. In this scenario, many, especially non-transiting, systems may experience flaring star-planet interaction, but those would not show up as correlation of flare timing with the orbital phase in our data.

Most of our systems are transiting, and for those we can expect this scenario to be a minor problem unless the latitude of the footpoint is very high. Of the systems that have high expected power but do not show any excess flaring, only TAP 26 b is a planet detected in radial velocity, and has a relatively high orbital inclination of about $55\pm10$ deg inferred from photometry, spectroscopy, and Zeeman Doppler measurements~\citep{yu2017hot}. Their ZD map reveals magnetic field concentrations close to the rotational pole, and the brightness maps also show a dark spot in the same location. If the orbital plane is aligned with the stellar rotation axis, the absence of phase-correlated flaring in TAP 26 could be explained by the footpoint of interaction being always in view, and therefore never modulated.

@@

\subsection{Tidal interaction}
\label{sec:discussion:tidal}
\begin{figure*}[t]
    \script{paper_tidal_interaction.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/PAPER_tidal_AD_test.png}
    \caption{Deviation from random flare times in phase with $P_{\rm orb}/2$, i.e., in phase with tidal bulges raised on the star, compared to different models of tidal interaction~(Section~\ref{sec:discussion:tidal}).
           \textbf{Left panel}: The tidal torque in the system for stars with a convective envelope. Blue color indicates that the star rotates slower than the planet orbits, so that angular momentum is transferred from the orbit to the spin of the star. Grey color is the reverse. \textbf{Middle panel}: The tidal dissipation timescale. \textbf{Right panel}:  Relative gravitational perturbation in the star.}
        \label{fig:tidal}
    \end{centering}
\end{figure*}

@@

\subsubsection{Locally expressed tidal interaction}
Tidal interaction can also lead to enhanced activity, globally, and locally.  Locally, we expect to see a periodicity with half the orbital period of the planet, corresponding to the two tidal bulges forming in the stellar envelope~\citep{cuntz2000stellar}. \citet{holzwarth2003dynamics} suggest an asymmetry induced in the stellar dynamo by the tidal disturbance, which leads to a preference for active (flaring) regions at longitudes about $P_{\rm orb}/2$ apart from each other.

@@

We cannot tell whether an additional individual flare is produced by tidal or magnetic interaction, but we can look for deviations from a random distribution of flare times in phase with the relevant period, i.e., $P_{\rm orb}/2$.

@@

The second model considers the tidal dissipation timescale -- the shorter the timescale, the higher the power of the interaction~\citep{zahn1977tidal}. Following~\citet{ilic2022tidal}, we adopt Eqn. 2 in~\citet{albrecht2012obliquities} for the tidal dissipation timescale in the convective envelope. We assume that all stars in our sample have a convective envelope because they flare, and flaring requires a dynamo-generated magnetic field, which can only operate in stars with convective envelopes. Most of our stars are dwarf stars below the Kraft break at spectral type F5~\citep{kraft1967studies}, except for KOI-12, which is an F5 sub-giant~\citep{frasca2016activity}.

@@

\subsubsection{Planetary and stellar masses}

We collect the planetary and stellar masses from the literature~(Table~\ref{tab:tidal}). For missing planetary masses, the radii were known, so we used the mass-radius relations implemented in \texttt{astro-forecaster}~[Ben Cassesse's implementation of \texttt{forecaster}][]\citep{chen2017probabilistic}. GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute Ks magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}. For Kepler-42 b, we used  $M_p=0.1-2.06M_\oplus$ that covers pure rock to pure iron compositions in \citet{muirhead2012characterizing}, and adopted the logarithmic mean for our estimate. Kepler-1558 c has a similar radius to Kepler-42 b, i.e., most likely a bare core planet, so we used density ranging from Earth bulk density to pure rock to estimate its mass. We also adopt the upper limit of $5M_J$ for HIP 67522, but use the lower error from \citet{chen2017probabilistic}.

@@

\paragraph{KOI-12,} which lacks signal with $P_{\rm orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction. This could be interpreted as KOI-12 b orbiting outside the Alfv\'en radius, so that it can still interact tidally, but not magnetically. However, we note that KOI-12 may be evolving off the main sequence, so that the tidal interaction scaling laws may not apply for this star.

@@

Overall, tidal interaction, if at all present, is less pronounced than magnetic SPI in our sample. However, if the observed deviations from intrinsic flaring do in fact represent low level tidal interaction signal, we can conclude that close-in planets can interact both magnetically and tidally. In line with theoretical considerations~\citep{strugarek2017fate}, our results tentatively suggest that magnetic interaction is more pronounced for planets with fast rotating, active hosts, while tidal interactions affect both systems with slowly and rapidly rotating stars.

@@

Applying both the stretch-and-break and Alfv\'en wing mechanisms for magnetic interaction, we found a tentative evidence trend between the expected power of interaction, and the presence of excess flaring in phase with the orbital period $P_{\rm orb}$. In particular, we found that there may be two branches at high expected power -- one where the measured excess flaring is correlated with the expected power, and one where excess flaring is absent. This may be an effect of the extent of the Alfv\'en surface, the intermittency in the interaction, or of the viewing geometry of the systems.

>>>>

\subsection{Flaring star-planet interaction signal}
\label{sec:results:spi}
We used the custom Anderson-Darling test introduced in Section~\ref{sec:methods:adtest} to look for flaring SPI in all systems with three or more flares with equivalent duration $ED>1\,$s, detected in their Kepler and TESS observations. We choose the $ED$ cutoff to make sure that we are comparing similar flares regardless of spectral type, that is, flares above the same energy relative to stellar luminosity, without losing too many flares. In~\citet{ilin2022searching}, AU Mic appeared to be more modulated with orbital period in the high energy flares above $1\,$s than below. It is also the only star in our sample, for which this threshold makes a difference in the significance of the Anderson-Darling test. However, we note that we lose five systems by applying this threshold -- GJ 393, Kepler-411, Kepler-138, GJ 1061, and Kepler-1084. We note that the flares (with $ED<1\,$s) in all of these systems are consistent with random flare phases within $1\sigma$.

@@

%The only single star system excluded is GJ 1061. The star is lacking a stellar rotation period estimate, which we need to calculate the magnetic field, and $v_{rel}$. \citet{dreizler2020reddots} estimate that it is a fairly slow rotator with a period between 50 and 200 days, so we do not expect it to have a strong magnetic field anyway. TURNS OUT IT DOES NOT HAVE ENOUGH FLARES FOR THE ANALYSIS

@@

\subsubsection{Proxima Cen}
\label{sec:results:individualstars:proxima}
We do not detect a deviation from intrinsic flaring on Proxima Cen, consistent with numerical models that place Proxima Cen b well outside the sub-Alfv\'enic zone~\citep{gomez2020earthlike, kavanagh2021planetinduced, garraffo2022revisiting}. However, this might not entirely exclude Proxima Cen from the search for flaring star-planet interaction. The tentatively detected Proxima Cen d, a planet further in, at 0.029 au, or 5 day orbital period~\citep{faria2022candidate, artigau2022linebyline} could still cause flaring star-planet interactions. Depending on the phase of the activity cycle, Proxima Cen d may be in the sub-Alf\'enic regime during Proxima Cen's activity maximum~\citep{gomez2020earthlike}. However, the orbital period of the tentative planet is so uncertain at this point that its coherence time~(Section~\ref{sec:results:coherence}) is shorter than the roughly 2yr observing baseline of Proxima Cen, preventing us from accurately measuring the flare phases.

@@

AU Mic is a 16-29 Myr old pre-main sequence M0-M1 dwarf with a strong magnetic field of about $3010\pm220\,$G obtained from Zeeman broadening measurements~\citep{reiners2022magnetism}. The innermost Neptune-sized planet, AU Mic b, could be both inside the sub-Alfv\'enic zone if the star's mass loss rate is relatively low at about 30 times the solar value or lower~\citep{alvarado-gomez2022simulating}. If the mass loss rate is high, exceeding the solar value by a factor of several hundreds, AU Mic b could orbit in the super-Alfv\'enic zone, and become unable to experience any planet-induced flaring. Recently, \citet{klein2022one} found tentative periodicity with the orbital period of AU Mic b in the chromospheric He I D line, which increases if the contribution from flares is included in the calculation. Overall, our marginal signal of flaring star-planet interaction in the AU Mic system supports the idea that this young, magnetically active M dwarf system with a close-in Neptune could exhibit planet-induced flaring.
For a detailed discussion of AU Mic and its flaring star-planet interaction, we refer to~\cite{ilin2022searching}, where we also estimate that an additional 50–100 days of TESS-like monitoring of AU Mic would yield a $3\sigma$ detection if the marginal signal in our data is real.

K2-25 is a multiplanet system around a fast rotating ($P_{\rm rot}<2\,$d) mid-M dwarf in the Hyades open cluster~\citep[600-800 Myr, ][]{stefansson2020habitable}. Both the expected power of interaction, and the measured deviation, are remarkably similar to the AU Mic system. Interestingly, K2-25 b is in a presumably similar environment to GJ 436 b, but does not show the atmospheric escape in Ly$\alpha$ that the latter famously exhibits, which might be due to high speed stellar winds that suppress atmospheric escape~\citep{rockcliffe2021lya, carolan2020dichotomy, vidotto2020stellar}. Further investigation of magnetic star-planet interactions, flaring or otherwise, in this system could add an important constraint on K2-25's wind properties by clarifying whether the planet orbits in- or outside the Alfv\'en radius, especially accounting for its moderately high eccentricity~(see also Section~\ref{sec:discussion:eccentricity}).

In Figure~\ref{fig:adtest_bp}, K2-25 and AU Mic form a cluster with TOI-540 -- a fast rotating M dwarf with its innermost planet in a $1.24\,$d orbit~\citep{ment2021toi}. Compared to the other two systems, its innermost planet is not a Neptune, but a rocky planet slightly smaller than Earth~\citep{ment2021toi}. It is a relatively smaller obstacle in the host's magnetic field, yet the interaction is expected to be of a similar magnitude due to the strongest inferred stellar magnetic field, and closest orbit among the three systems.

@@

\subsubsection{KOI-12}
\label{sec:results:individualstars:koi12}
KOI-12, also known as Kepler-448, is a two-planet system with an eccentric outer planet KOI-12 c, and an inner Warm Jupiter planet KOI-12 b in a $17.8\,$d orbit~\citep{masuda2017eccentric}. With respect to rotation rate, stellar and planetary radius, the KOI-12 system is similar to HIP~67522 and TAP~26 (although for the those young stars the radii are large because the stars are still contracting onto the main sequence). In constrast, KOI-12 is $1.4\pm0.3\,$Gyr old~\citep{bourrier2015sophie}, an F5 subgiant~\citep{frasca2016activity}, which is already evolving off the main sequence. Yet, despite its high expected power of interaction, we detect no excess flaring in phase with KOI-12 b. Here, the reason could be that KOI-12 b is in fact super-Alfv\'enic due to the relatively wide orbit compared to TAP 26 and HIP 67522. However, our estimate of the Alf\'en radius place KOI-12 b in the sub-Alfv\'enic regime~(see Fig.~\ref{fig:as}), although the scaling law applied there may be inaccurate for post-main sequence stars. Intermittent interaction might play a role here as well, and could be favored if future observations capture episodes during which the interaction is 'on'.

@@

\subsection{Eccentricity}
\label{sec:discussion:eccentricity}
Orbital eccentricity can affect magnetic SPI by modulating the planet's distance to the star. If the planetary orbit is highly eccentric, the difference between periastron and apoastron can be significantly larger than the variability of the Alfv\'en radius. If then apoastron is outside this radius, and periastron within, the planet may find itself in the sub-Alfv\'enic zone only for a short amount of time, during the planet's rapid periastron passage. This was previously exploited in the case of HD 17156~\citep{maggio2015coordinated}, and analogously for the colliding magnetospheres in binary systems~\citep{massi2002periodic,getman2016search}. In our sample, the estimates for eccentricities of the innermost planets are all moderate to low, with $e\leq 0.35$. The exception is K2-25, with a relatively high $e\approx0.43$. If periastron passage in K2-25 occurs when the planet is in front of the star relative to the observer, the visibility effect of the interaction footpoint is further increased by the narrow phase range of the periastron passage. \citet{stefansson2020habitable} estimated the argument of periastron $\omega=120^{+12}_{-14}\,$deg for K2-25 (with longitude of the ascending node chosen such that $\omega$ is the same as the longitude of periastron, with $\omega=90\,$deg being periastron passage during transit,~\citealt{kipping2010investigations,dawson2012photoeccentric}). We can therefore conjecture that the tentative signal of flaring SPI in K2-25 is enhanced by eccentricity. Statistically, we are more likely to observe a planetary transit close to periastron, since periastron permits more orbital inclinations than apoastron. So, overall, we expect eccentric transiting systems to experience elevated SPI signal.

@@

Consider a system, where orbit, and stellar spin and stellar magnetic dipole are aligned. If the magnetic footpoint's latitude is low, i.e., close to the orbital plane, the orbital plane can be inclined to a high degree, and the footpoint will still periodically move in and out of view. However, if the footpoint's latitude is high, we need to observe the star-planet system nearly edge-on to be able to measure a modulation of activity with the planet's orbital phase. Assuming the dipole field dominates at the distance of the planet, the footpoint will be close to the pole, similar to the UV spot created by Io and the other moons in the polar cap of Jupiter~\citep{clarke1996farultraviolet, prange1996rapid}. In this scenario, many, especially non-transiting, systems may experience flaring star-planet interaction, but those would not show up as correlation of flare timing with the orbital phase in our data.

Most of our systems are transiting, and for those we can expect this scenario to be a minor problem unless the latitude of the footpoint is very high. Of the systems that have high expected power but do not show any excess flaring, only TAP 26 b is a planet detected in radial velocity, and has a relatively high orbital inclination of about $55\pm10$ deg inferred from photometry, spectroscopy, and Zeeman Doppler measurements~\citep{yu2017hot}. Their ZD map reveals magnetic field concentrations close to the rotational pole, and the brightness maps also show a dark spot in the same location. If the orbital plane axis is aligned with the stellar rotation axis, the absence of phase-correlated flaring in TAP 26 could be explained by the footpoint of interaction being always in view, and therefore never modulated.

@@

\subsection{Tidal interaction}
\label{sec:discussion:tidal}
\begin{figure*}[t]
    \script{paper_tidal_interaction.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/PAPER_tidal_AD_test.png}
    \caption{Deviation from random flare times in phase with $P_{\rm orb}/2$, i.e., in phase with tidal bulges raised on the star, compared to different models of tidal interaction~(Section~\ref{sec:discussion:tidal}). \textbf{Cross symbols} mark planets with $M_p \sin i$ measurements. \textbf{Round symbols} mark planets with measured  or estimated $M_p$ (see Section~\ref{sec:discussion:mpms}). 
           \textbf{Left panel}: The tidal torque in the system for stars with a convective envelope. Blue color indicates that the star rotates slower than the planet orbits, so that angular momentum is transferred from the orbit to the spin of the star. Grey color is the reverse. \textbf{Middle panel}: The tidal dissipation timescale. \textbf{Right panel}:  Relative gravitational perturbation in the star.}
        \label{fig:tidal}
    \end{centering}
\end{figure*}

@@

\subsubsection{Locally expressed tidal interaction}
Tidal interaction can also lead to enhanced stellar activity, globally, and locally, e.g., higher coronal emission~\citep{ilic2022tidal}, or excess flaring. Locally, we expect to see a periodicity of activity with half the orbital period of the planet, corresponding to the two tidal bulges forming in the stellar envelope~\citep{cuntz2000stellar}. \citet{holzwarth2003dynamics} suggest an asymmetry induced in the stellar dynamo by the tidal disturbance, which could lead to a preference for active regions (potentially flaring) at longitudes about $P_{\rm orb}/2$ apart from each other.

@@

We cannot tell whether an additional individual flare is triggered by tidal or magnetic interaction, but we can look for deviations from a random distribution of flare times in phase with the relevant period, i.e., $P_{\rm orb}/2$.

@@

The second model considers the tidal dissipation timescale -- the shorter the timescale, the higher the power of the interaction~\citep{zahn1977tidal}. Following~\citet{ilic2022tidal}, we adopt Eqn. 2 in~\citet{albrecht2012obliquities} for the tidal dissipation timescale in the convective envelope. We assume that all stars in our sample have a convective envelope because they flare, and flaring requires a dynamo-generated magnetic field, which can only operate in stars with convective envelopes or fully convective stars. Most of our stars are dwarf stars below the Kraft break at spectral type F5~\citep{kraft1967studies}, except for KOI-12, which is an F5 sub-giant~\citep{frasca2016activity}.

@@

\subsubsection{Planetary and stellar masses}
\label{sec:discussion:mpms}
We collect the planetary and stellar masses from the literature~(Table~\ref{tab:tidal}). For missing planetary masses, the radii were known, so we used the mass-radius relations implemented in \texttt{astro-forecaster}~[Ben Cassesse's implementation of \texttt{forecaster}][]\citep{chen2017probabilistic}. GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute Ks magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}. For Kepler-42 b, we used  $M_p=0.1-2.06M_\oplus$ that covers pure rock to pure iron compositions in \citet{muirhead2012characterizing}, and adopted the logarithmic mean for our estimate. Kepler-1558 c has a similar radius to Kepler-42 b, i.e., most likely a bare core planet, so we used density ranging from Earth bulk density to pure rock to estimate its mass. We also adopt the upper limit of $5M_J$ for HIP 67522, but use the lower error from \citet{chen2017probabilistic}. The assumptions we made here are conservative, and the estimates based on \citet{chen2017probabilistic} use a broad sample of planets, so we consider the planetary mass estimates with their respective uncertainties robust. We note, however, that the mass estimates for RV-detected planets are $M_p \sin i$, so that their expected interaction may be stronger than indicated in Fig.~\ref{fig:tidal}.

@@

\paragraph{KOI-12,} which lacks signal with $P_{\rm orb}$ despite high expected power of magnetic interaction, shows elevated expected and measured tidal interaction. However, we note that KOI-12 may be evolving off the main sequence, so that the tidal interaction scaling laws may not apply for this star.

@@

Overall, tidal interaction, if at all present, is less pronounced than magnetic SPI in our sample. However, if the observed deviations from intrinsic flaring do in fact represent low level tidal interaction signal, we can conclude that close-in planets can interact both magnetically and tidally. In line with theoretical considerations~\citep{strugarek2017fate}, our results tentatively suggest that magnetic interaction is more pronounced for planets with fast rotating, active hosts, while tidal interactions affect both systems with slowly and rapidly rotating stars. Finally, exceptions such as TAP 26 exemplify that the simple scaling laws we applied here may not capture the complexity of the interaction.

@@

Applying both the stretch-and-break and Alfv\'en wing mechanisms for magnetic interaction, we found a tentative evidence trend between the expected power of interaction, and the presence of excess flaring in phase with the orbital period $P_{\rm orb}$. In particular, we found that there may be two branches at high expected power -- one where the measured excess flaring is correlated with the expected power, and one where excess flaring is absent. This may be, among others, an effect of the extent of the Alfv\'en surface, the intermittency in the interaction, or of the viewing geometry of the systems.
